---
title: "Practice makes perfect "
author: "XXX" 
date: today 
project: 
  output-dir: Output
  execute-dir: project
toc: true 
abstract-title: "Research question:"
abstract: "......"
format: 
  html: 
    embed-resources: true
    number-sections: true
    code-fold: true
editor: visual 
editor_options: 
  chunk_output_type: console
execute:
  warning: false 
  message: false
  freeze: false 
---

# Prepare Phase

Load the required libraries, import, screen and correct the data.

```{r}
#| label: prepare session 

  library(pastecs)
  library(ggplot2)
  library(ggpubr); theme_set(theme_bw())
  library(GGally)
  library(performance)
  library(MuMIn)
  library(ggeffects)
  library(tidyverse)
  library(broom)
  library(car)

  library(knitr)                                     # To render tables

# Import data
  soup <- read.csv("~/Desktop/Practice_10/Data/raw/SpicySoup.csv", stringsAsFactors= T) 
#if there is a coloumn in the table  that has non-numeric values do stringsasfactors = T so they convert into factors --> VERY ideal for modeling 
# Factors are what R uses for categorical variables in models (like treatment groups).
  
# clean and unterstand data 
# data$col <- ifelse(data$col == "Yes", 1, 0) --> if data column is no/yes and you need 1/0 for fiting models!!!
str(soup) # shows data typ and preview of the columns
summary(soup) #numeric → mean, min, max, etc.+ factors → counts per category

# Add an additional column to express the proportion of success in each batch of trials
  soup$prop<- soup$successes/soup$n_trials
```

## Explore the data

It's always a good idea to get to know your data, both by exploring them numerically and graphically. Since I asked you to write the units of the variables in the main text (because one of them contains a Greek letter), let's give that a go:

-   [baseline is measured in ]{style="color: darkblue"}$\mu$[g/mL]{style="color: darkblue"}

-   temperature messured in °C

### Numerically

In @tbl-explore-data we see descriptive statistics for the variables of interest.

```{r}
#| label: tbl-explore-data
#| tbl-cap: "Descriptive statistics for the variables of interest"
#| echo: false 

# Numerically take 
 sum_stats<-
   stat.desc(soup[, c("successes", "temp", "spice", "n_trials", "prop")], norm= T)
 
 kable(sum_stats, digits= 1)

cor(soup$spice , soup$successes)
cor(soup$temp , soup$successes)
```

### Graphically

```{r}
#| label: fig-graphs-1
#| fig-cap: "good graph"
#| echo: false 


# Another option is too Scatterplot matrix
ggpairs(soup[, c("temp", "spice", "prop", "successes", "n_trials")])
```

```{r}
#| label: fig-graph1
#| fig-caption: "beutiful figure"
#| fig-width: !expr 16/2.54 #I want my figure in 16 cm whatever size it is?
#| fig-height: !expr 9/2.54
#| code-fold: true

# Draw a graph that captures the research question - shows us a better overview 

ggarrange(
    ggplot(soup, aes(spice, prop)) +
      geom_point(aes(size= n_trials), alpha= .4, col= "blue") +
      geom_smooth(method= glm, method.args= list(family= "binomial"),
                  col= "black") +
      labs(x= expression("Spiciness (" * mu * "g/ml)"), #dollar notation for mu applies only for markdown not for R code 
           y= "Proportion of patients with\n enhanced immune repsonse",
           size= "Trial size"),
    ggplot(soup, aes(temp, prop)) +
      geom_point(aes(size= n_trials), alpha= .4, col= "blue") +
      geom_smooth(method= glm, method.args= list(family= "binomial"),
                  col= "black") +
      labs(x= "Serving temperature (°C)",
           y= "Proportion of patients with\n enhanced immune repsonse",
           size= "Trial size"),
    nrow= 1, ncol= 2, common.legend= T, labels= c("a)", "b)"))
```

## Fit model

### Formulate and compare

Now it's time to fit and compare some models (@tbl-model-comparison). As the output is in counts we will make glm models. With these data, it is quite difficult to decide which model to prefer, however, since the hypothesis involved an interaction term, lets continue with that model, `model.04`.

```{r}
#| label: tbl-model-comparison 
#| tbl-cap: "model comparison"

model.00 <- glm(prop ~ 1, weights= n_trials, family = binomial, data = soup) # weights = n_trials = number of Bernoulli trials behind each proportion! 
model.01 <- glm(prop ~ spice, weights= n_trials, family = binomial, data = soup)

model.02 <- glm(prop ~ temp, weights= n_trials, family = binomial, data = soup)

model.03 <- glm(prop ~ spice + temp, weights= n_trials, family = binomial, data = soup)

model.04 <- glm(prop ~ spice * temp, weights= n_trials, family = binomial, data = soup)

#compare models 
kable(compare_performance(model.00, model.01, model.02, model.03, model.04), digits= 3) # Use AICc to decide: small sample!!! small AIC/ AICc indicate best model
```

### Validate the preferred model

Great, we've decided on "the best" model given the data at hand, but it might still be a bad fit to our data. Let's make sure we can trust our selected model first, before we try to interpret it.

```{r}
#| label: validate model 

#validate model 
check_overdispersion(model.04)
```

```{r}
#| label: fig-diagnostic-plots
#| fig-cap: "Model diagnostics: these look pretty good "
#| fig-width: !expr 25/2.54
#| fig-height: !expr 30/2.54
#| echo: false 

#validate model 
check_model(model.04)

# Collinearity check on model without interaction
#plot(check_collinearity(model.03))                   # Looks good!

summary(model.04)
```

## Interpret model

```{r}
#| label: fig-interpret-objects
#| fig-cap: "effectiveness of the treatments"
#| echo: false 

##| output: false --> output graph would not be shown

# Objects to construct table 

## Coefficients, SE, z and p -----
  coef.table<- round(summary(model.04)$coefficients, 3)

## Approximate R2 ----- amount of variablity explained by your model
  r.2<- round(attributes(r.squaredLR(model.04))$adj.r.squared, 3)  

## Compare performance to null-model ----- stored the anova of glm.00 and gln.02 in null.chi - - in quarto you extract number from model and store them in objects/names like null.chi
  null.chi<- anova(model.04)

# Objects to plot predictions -----------------------------------------------

## Interaction plot -----
  # Create vector of values for x-axis (to get smooth lines) which is baseline => x variable 
  t.vec<- seq(min(soup$temp), max(soup$temp), length.out= 100)
  
  summary(soup$spice) #manually enter min, mean, max bellow 

 # Create predictions dataframe
  pred.int<- predict_response(model.04,
                              c("temp [t.vec]",
                                "spice [0.1, 4.06, 7.9]"))
  # Assign text labels to the three spice groups
  levels(pred.int$group)<- c("min", "mean", "max")
  
  # Create plot - created a plot which is stored under the name pred.plot 
  pred.plot<- ggplot(pred.int, aes(x, predicted)) +
    geom_point(data= soup, aes(temp, prop, size= n_trials), alpha= .4) +
    geom_ribbon(aes(ymin= conf.low, ymax= conf.high,
                    fill= group), alpha= .2) +
    geom_line(aes(col= group)) +
    labs(x= "Serving temperature\n of the soup (°C)", #added line break with \n!!!!
         y= "Proportion of patients with\n enhanced immune response",
         size= "Trial size", col= "Spiciness", fill= "Spiciness") +
    coord_cartesian(ylim= c(0, 1))

```

```{r}
#| label: tbl-glm 
#| tbl-cap: !expr paste("Estimates, associated standard errors and statistical significance of the parameters estimated by a binomial GLM.", "($R^2$=", r.2, ", $\\chi^2_{(", null.chi[2, 3], ",", null.chi[2, 1], ")}$=", round(null.chi[2,4], 3), ", $p$", format.pval(null.chi[2, 5], eps = 0.001), ")") 
#refering to object in table caption is a pain look above - so if something in data changes, it will updated by itself - important for GRP: reproducibiltiy and transparancy !! 
# Create table
kable(coef.table)
```

```{r}
#| label: fig-predict
#| fig-cap: "Raw data and model predictions to visualize the relationship between the propotion of patients that exhibited an elevated immune response, and the temperature and spicyness of the soup."
#| fig-width: !expr 15/2.54
#| fig-height: !expr 9/2.54

# Plot predictions
  pred.plot

```
